---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = F,
  error = F
)

library(readr)
library(tidyverse)
Species <- read_csv("https://raw.githubusercontent.com/derek-corcoran-barrios/OikosRepoducibleResearch/master/Species.csv")

```

# ExampleReproducibleResearch

<!-- badges: start -->

<!-- badges: end -->

The goal of ExampleReproducibleResearch is to make an example repository where I will work through examples of reproducible research. I will explore the species dataset in order to try to find *relationships* between their abundance and **enviromental variables**.

For exmaple in the following figure we will se the relationship between the abundance of species 4 and annual mean temperature

```{r plotspp4temp, fig.cap="Temperature vs Abundance"}
ggplot(Species, aes(x = bio_1, y = abund_sp4)) + geom_point() + theme_bw()
```

In our dataset the number of observatios is `r prettyNum(nrow(Species), big.mark = ",")`, the mean temperature in the sites is `r round(mean(Species$bio_1), 2)`
